Inferring fine scale wild species distribution from spatially aggregated data

### 2022-10-21 Version_M2_plusieurszones/pres/AFH_2022/AFH_2022.tex
modif

---
title: "Inferring fine scale wild species distribution from spatially aggregated data"
author : "Marie-Pierre Etienne, Baptiste Alglave, Kasper Kristensen, Youen Vermard, Mathieu Woillez, Etienne Rivot"

fontsize: 10pt
bibliography : ["ref.bib"]
csl : ices-journal-of-marine-science.csl

output:
  beamer_presentation:
    theme: "Darmstadt"
    colortheme: "default"
    slide_level: 3
    # template: mytemplate.tex
    includes:
      in_header: header-simple.tex
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyr)
library(rnaturalearth)
library(stringr)
library(sf)
library(raster)
library(maps)
library(mapdata)
library(ggplot2)
library(ggspatial)
library(cowplot)
library(latex2exp)
library(ggpubr)

col_scale <- function(palette = "Spectral", name = "", limits = NULL) {
  scale_colour_distiller(palette = palette,   # spectral colour scale
                         guide = "colourbar", # continuous colour bar
                         name = name,
                         limits = limits)
}

run_codes <- F

grid_projection <- "+proj=longlat +datum=WGS84"

mapBase <- map("worldHires", fill = T, plot = F)
mapBase <- st_as_sf(mapBase) %>% filter(ID %in% c("France","Spain"))

```

# Context

### Spatial data in ecology

<!-- Standardized and high quality data, but low amount of samples -->
<!-- more data, but no standardize sampling plan (e.g. problem related to preferential sampling) -->
<!-- legal and massive data, but low quality, declared at the level of some administrative unit -->

@@

---
<!-- \btVFill -->
\begin{center} \Large
\textbf{How to integrate all these datasources?}
\end{center}
\large
(especially when they do not have the same spatial resolution)
\normalsize

@@

# Material and method

### Commercial catch declarations data in fishery science

```{r,echo=F,fig.align='center',out.width="120%"}

if(run_codes){

  load("map/ICES_rect.RData")
  load("res/points_sf.RData")

  #-------------------
  ## Logbook data plot
  #-------------------
  logbooks_df <- points_sf %>%
    # filter(str_detect(SI_DATE,"11/2018")) %>%
    group_by(ICESNAME_1) %>%
    dplyr::summarise(Catch = sum(LE_KG_Solea_solea)/1000,
                     Effort = sum(INTV)/60)

  logbooks_sf <- st_join(ICES_rect,logbooks_df) %>%
    filter(!is.na(Effort))

  Logbooks_data <- ggplot()+
    geom_sf(data = ICES_rect,fill="skyblue",alpha=0.25)+
    geom_sf(data=logbooks_sf,aes(fill=Catch))+
    geom_sf(data = mapBase)+
    scale_fill_distiller(palette = "Spectral")+
    theme(panel.background = element_rect(fill = "skyblue"),
          plot.title = element_text(hjust=0.5),
          legend.position = "none")+
    geom_sf(col="black")+
    coord_sf(xlim = c(-6,0), ylim = c(43,48), expand = FALSE)+
    annotation_scale(location = "bl", line_width = .5)+
    annotation_north_arrow(location = "tl", height = unit(0.7, "cm"),
                           width = unit(0.7, "cm"))

  ggsave(Logbooks_data,filename = "images/logbooks_data.png",width = 5,height = 5)

  #---------------
  ## VMS data plot
  #---------------
  ## Aggregate/discretize data
  vms_df <- points_sf %>%
    mutate(long = sf::st_coordinates(.)[,1],
           lati = sf::st_coordinates(.)[,2]) %>%
    as.data.frame %>%
    dplyr::select(-geometry) %>%
    mutate(long = round(long,digits = 2),
           lati = round(lati,digits = 2)) %>%
    group_by(long,lati) %>%
    dplyr::summarise(Effort = sum(INTV)/60)

  vms_sf <- st_as_sf(vms_df,coords = c("long","lati"),crs=grid_projection)

  ## Build polygon
  # Coordinates Bay of Biscay
  grid_xmin <- -6
  grid_xmax <- 0
  grid_ymin <- 42
  grid_ymax <- 48
  grid_limit <- extent(c(grid_xmin,grid_xmax,grid_ymin,grid_ymax))

  # Build grid
  grid <- raster(grid_limit)
  res(grid) <- 0.025
  crs(grid) <- "+proj=longlat +datum=WGS84"
  gridpolygon <- rasterToPolygons(grid)
  gridpolygon$layer <- c(1:length(gridpolygon$layer))
  gridpolygon_sf <- st_as_sf(gridpolygon)

  vms_sf_2 <- st_join(gridpolygon_sf,points_sf)
  vms_sf_3 <- vms_sf_2 %>%
    group_by(layer) %>%
    dplyr::summarise(Effort = sum(INTV)/60)

  vms_sf_3 <- vms_sf_3 %>%
    filter(!is.na(Effort))

  # save(data=vms_sf_3,file="res/vms_sf_3.RData")

  vms_data <- ggplot()+
    geom_sf(data = ICES_rect,fill="skyblue",alpha=0.25)+
    geom_sf(data=vms_sf_3,aes(col=Effort,fill=Effort))+
    geom_sf(data = ICES_rect,alpha=0)+
    geom_sf(data = mapBase)+
    scale_color_distiller(direction = 1,palette = "OrRd")+ # palette = "OrRd"
    scale_fill_distiller(direction = 1,palette = "OrRd")+ # ,palette = "Spectral"
    theme(panel.background = element_rect(fill = "skyblue"),
          plot.title = element_text(hjust=0.5),
          legend.position = "none")+
    geom_sf(col="black")+
    coord_sf(xlim = c(-6,0), ylim = c(43,48), expand = FALSE)

  ggsave(filename = "images/vms_data.png",width = 5,height = 5)

```

@@

### Two alternative procedures to reallocate catches

@@

### Two alternative procedures to reallocate catches

\textbf{Punctual observation model} ($Y_i$)

\scriptsize $\operatorname{L}(y,\mu,\sigma^2)$ is the lognormal likelihood for observation $y$, mean $\mu$ and variance $\sigma^2$

$Y$ and $D$ are supposed conditional on S and x \footnotesize

$$
\operatorname{P}\left(Y_i=y_{i} \right) =
\left\{
    \begin{array}{ll}
        p_i & \text { if } y_{i}=0 \\
        \left(1-p_i\right) \cdot \operatorname{L}\left(y_{i },\mu_i=\frac{S(x_i)}{\left(1 - p_i\right)},\sigma^{2} \right) & \text { if } y_{i} > 0
    \end{array}
\right.
$$

$$p_{i}=\exp(-e^\xi .S(x_{i}))$$

@@

### Specifying $\operatorname{P}\left(D_j=d_{j} \vert d_j > 0 \right)$

@@

$$E(D_j \vert d_j > 0)=\frac{\sum_{i \in \mathcal{P}_j} S(x_{i})}{1-\pi_j}$$

$$Var(D_j \vert d_j > 0) = \frac{\sum_{i \in \mathcal{P}_j} Var(Y_{i})}{1-\pi_j} - \frac{\pi_j}{(1-\pi_j)^2}E(D_j)^2$$

$$Var(Y_{i})=\frac{S(x_{i})^2}{1-p_{i}}(e^{\sigma^2}-(1-p_{i}))$$

@@

### Simulation-estimation and case study

```{r,echo=F}

if(run_codes){
  ## Load simulated data
  load("res/simu_df.RData")
  load("res/list_input.RData")

  simu_df_2 <- simu_df %>%
    mutate(Ab = sum(S_x))

  loc_x <- list_input$loc_x
  sci.data_df <- data.frame(cell = list_input$index_sci_i,
                            y_sci = list_input$y_sci_i) %>%
    inner_join(loc_x[,c("x","y","cell","ICESNAME")])

  com.data_df <- data.frame(cell = list_input$index_i,
                            y_com = list_input$y_i2) %>%
    inner_join(loc_x[,c("x","y","cell","ICESNAME")]) %>%
    group_by(x,y,cell,ICESNAME) %>%
    dplyr::summarise(n=n())

  ## Grid data
  grid <- raster(grid_limit)
  res(grid) <- 0.05
  crs(grid) <- "+proj=longlat +datum=WGS84"
  gridpolygon <- rasterToPolygons(grid)
  gridpolygon$layer <- c(1:length(gridpolygon$layer))
  gridpolygon_sf <- st_as_sf(gridpolygon)

  simu_sf <- st_as_sf(simu_df_2,coords = c("long","lati"),crs=grid_projection)

  simu_sf_2 <- st_join(gridpolygon_sf,simu_sf) %>%
    filter(!is.na(S_x))

  ## Plot data
  data_plot <- ggplot()+
    geom_sf(data=simu_sf_2,aes(fill=log(S_x)),col=NA,alpha=0.5)+
    geom_sf(data=simu_sf_2[which(simu_sf_2$ICESNAME %in% com.data_df$ICESNAME),],
            aes(fill=log(S_x),col=log(S_x)))+
    scale_fill_distiller(palette = "Spectral")+
    scale_color_distiller(palette = "Spectral")+
    geom_point(data=sci.data_df,aes(x=x,y=y),fill="#619CFF",shape=21,size=1)+
    theme_bw()+
    theme(plot.title = element_text(hjust = 0.5),
          plot.subtitle = element_text(hjust = 0.5),
          legend.title = element_blank(),
          legend.position = "none")+
    geom_sf(data=ICES_rect,alpha=0)+
    geom_sf(data = mapBase)+
    coord_sf(xlim = c(-6,0), ylim = c(43,48), expand = FALSE)+
    xlab("")+ylab("")

  ggsave(filename = "images/data_plot.png",width = 5,height = 5)

```

@@

# Results

### Simulation-estimation

```{r,echo=F}

if(run_codes){

  ######################
  ## Parameter estimates
  ######################
  load("res/Results_full_multi_square.RData")

  Results_plot <- Results_2 %>%
    filter(converge == 0) %>%
    filter(simu_type == "Unsampled Rectangles")

  Results_plot[,"RelBias_N"]=(Results_plot[,"N_est"]-Results_plot[,"N_true"])/Results_plot[,"N_true"]
  Results_plot[,"RelBias_N.2"]=(Results_plot[,"N_est.2"]-Results_plot[,"N_true.2"])/Results_plot[,"N_true.2"]
  Results_plot[,"RelBias_beta"]=(Results_plot[,"beta1_est"]-Results_plot[,"beta1_true"])/Results_plot[,"beta1_true"]

  Results_plot$obs <- NA
  Results_plot$obs[which(Results_plot$aggreg_obs == T)] <- "Dj"
  Results_plot$obs[which(Results_plot$aggreg_obs == F)] <- "Yi*"
  Results_plot$obs[which(Results_plot$Estimation_model == 2)] <- "Scientific model"
  Results_plot$obs <- factor(Results_plot$obs,levels = c("Yi*","Dj","Scientific model"))

  Results_plot$Model[which(Results_plot$Model == "Scientific model")] <- "Scientific"
  Results_plot$Model[which(Results_plot$Model == "Commercial model")] <- "Commercial"
  Results_plot$Model[which(Results_plot$Model == "Integrated model")] <- "Integrated"

  Results_plot <- Results_plot %>%
    filter(Model != "Commercial")

  # Results_plot_fullArea <- Results_plot
  # Results_plot_UnsampArea <- Results_plot

  beta_plot <- ggplot()+
    geom_boxplot(data = Results_plot,
                 aes(x = Model,
                     y = beta1_est,
                     fill = obs))+
    geom_hline(yintercept = 0,linetype="dashed")+
    theme_bw()+
    theme(legend.title = element_blank(),
          legend.position = "none",
          aspect.ratio = 1)+
    # facet_wrap(.~simu_type)+
    ylab(TeX("$\\beta_S$")) +
    xlab("")+
    geom_hline(yintercept = 2,col="red",linetype="dashed")+
    scale_color_manual(breaks = c("Scientific model",
                                  "Yi*",
                                  "Dj"),
                       values=c("#619CFF","#F8766D","#00BA38"))

  MSPE_S_plot <- ggplot()+
    geom_boxplot(data = Results_plot,
                 aes(x = Model,
                     y = mspe,
                     fill = obs))+
    theme_bw()+
    theme(legend.title = element_blank(),
          legend.position = "none",
          aspect.ratio = 1)+
    # facet_wrap(.~simu_type)+
    ylab("MSPE")+xlab("")+
    scale_color_manual(breaks = c("Scientific model",
                                  "Yi*",
                                  "Dj"),
                       values=c("#619CFF","#F8766D","#00BA38"))+
    ylim(0,NA)

  legend <- as_ggplot(cowplot::get_legend(MSPE_S_plot+theme(legend.position="bottom",legend.title = element_blank())))

  pl_plot <- plot_grid(MSPE_S_plot,
                       beta_plot,
                       ncol = 1,
                       legend,
                       align="hv",
                       rel_heights = c(1,1,0.15))

  ggsave(filename = "images/res_simu_plot.png",width = 4,height = 7.5)

  #######
  ## Maps
  #######
  simu_plot <- ggplot(simu_df)+
    geom_point(aes(x=x,y=y,col=S_x/sum(S_x)),shape=15,size=2)+
    scale_color_distiller(palette = "Spectral")+
    ggtitle("Simulated latent field")+
    theme_bw()+
    theme(plot.title = element_text(hjust = 0.5,face = "bold"),
          plot.subtitle = element_text(hjust = 0.5),
          legend.position = "none")+
    geom_sf(data = mapBase)+
    coord_sf(xlim = c(-6,0), ylim = c(43,48), expand = FALSE)+
    xlab("")+ylab("")

  load("res/fit_IM_res_sci.RData")
  sci_df <- data.frame(loc_x,S_x=fit_IM_res$Report$S_x)
  sci_plot <- ggplot(sci_df)+
    geom_point(aes(x=x,y=y,col=S_x/sum(S_x)),shape=15,size=2)+
    scale_color_distiller(palette = "Spectral")+
    ggtitle("Scientific model")+
    theme_bw()+
    theme(plot.title = element_text(colour = "#619CFF",hjust = 0.5,face = "bold"),
          plot.subtitle = element_text(hjust = 0.5),
          legend.position = "none")+
    geom_sf(data = mapBase)+
    coord_sf(xlim = c(-6,0), ylim = c(43,48), expand = FALSE)+
    xlab("")+ylab("")

  load("res/fit_IM_res_int_Yi.RData")
  int_Yi_df <- data.frame(loc_x,S_x=fit_IM_res$Report$S_x)
  int_Yi_plot <- ggplot(int_Yi_df)+
    geom_point(aes(x=x,y=y,col=S_x/sum(S_x)),shape=15,size=2)+
    scale_color_distiller(palette = "Spectral")+
    ggtitle("Commercial likelihood on Yi*")+
    theme_bw()+
    theme(plot.title = element_text(colour = "#F8766D",hjust = 0.5,face = "bold"),
          plot.subtitle = element_text(hjust = 0.5),
          legend.position = "none")+
    geom_sf(data = mapBase)+
    coord_sf(xlim = c(-6,0), ylim = c(43,48), expand = FALSE)+
    xlab("")+ylab("")

  load("res/fit_IM_res_int_Dj.RData")
  int_Dj_df <- data.frame(loc_x,S_x=fit_IM_res$Report$S_x)
  int_Dj_plot <- ggplot(int_Dj_df)+
    geom_point(aes(x=x,y=y,col=S_x/sum(S_x)),shape=15,size=2)+
    scale_color_distiller(palette = "Spectral")+
    ggtitle("Commercial likelihood on Dj")+
    theme_bw()+
    theme(plot.title = element_text(colour = "#00BA38",hjust = 0.5,face = "bold"),
          plot.subtitle = element_text(hjust = 0.5),
          legend.position = "none")+
    geom_sf(data = mapBase)+
    coord_sf(xlim = c(-6,0), ylim = c(43,48), expand = FALSE)+
    xlab("")+ylab("")

  map_simu <- plot_grid(simu_plot,sci_plot,int_Yi_plot,int_Dj_plot)

  ggsave(filename = "images/map_simu_plot.png",width = 6,height = 7.5)

```

@@

### Case study: Sole in the Bay of Biscay

```{r,echo=F}

if(run_codes){

  ## Load data
  load("res/sci_df.RData")

  load("res/realloc_rest_df.RData")

  load("res/no.realloc_df.RData")

  load("res/est_par_df_full_3.RData")

  ## Plot maps
  no.realloc_plot <- ggplot(no.realloc_df)+
    geom_point(aes(x=x,y=y,col=S_x),shape=15,size=2)+
    scale_color_distiller(palette = "Spectral",limits=c(0,NA))+
    ggtitle("Commercial likelihood on Yi*")+
    theme_bw()+
    theme(legend.position = "none",
          plot.title = element_text(colour = "#F8766D",hjust = 0.5,face = "bold"))+
    geom_sf(data = mapBase)+
    coord_sf(xlim = c(-6,0), ylim = c(43,48), expand = FALSE)+
    xlab("")+ylab("")

  realloc_rest_plot <- ggplot(realloc_rest_df)+
    geom_point(aes(x=x,y=y,col=S_x),shape=15,size=2)+
    scale_color_distiller(palette = "Spectral",limits=c(0,NA))+
    ggtitle("Commercial likelihood on Dj")+
    theme_bw()+
    theme(legend.position = "none",
          plot.title = element_text(colour = "#00BA38",hjust = 0.5,face = "bold"))+
    geom_sf(data = mapBase)+
    coord_sf(xlim = c(-6,0), ylim = c(43,48), expand = FALSE)+
    xlab("")+ylab("")

  sci_plot <- ggplot(sci_df)+
    geom_point(aes(x=x,y=y,col=S_x),shape=15,size=2)+
    scale_color_distiller(palette = "Spectral",limits=c(0,NA))+
    ggtitle("Scientific model")+
    theme_bw()+
    theme(legend.position = "none",
          plot.title = element_text(colour = "#619CFF",hjust = 0.5,face = "bold"))+
    geom_sf(data = mapBase)+
    coord_sf(xlim = c(-6,0), ylim = c(43,48), expand = FALSE)+
    xlab("")+ylab("")

  # plot(log(no.realloc_df$S_x),log(sci_df$S_x))
  # cor(log(no.realloc_df$S_x),log(sci_df$S_x),method = "spearman")
  # plot(log(realloc_rest_df$S_x),log(sci_df$S_x))
  # cor(log(realloc_rest_df$S_x),log(sci_df$S_x),method = "spearman")

  case_study_plot <- plot_grid(NULL,sci_plot,no.realloc_plot,realloc_rest_plot,align="hv")

  ggsave("images/case_study_plot.png",width = 6, height = 7.5)

  ## Parameter estimates
  est_par_df_full_3$lkl[which(est_par_df_full_3$lkl == "Yi")] <- "Yi*"
  est_par_df_full_3$lkl <- factor(est_par_df_full_3$lkl,levels = c("Dj","Yi*","Scientific model"))
  est_par_df_full_3 <- est_par_df_full_3 %>%
    filter(par_names != "substr_Sand_Coarse_substrate")
  par_plot <- ggplot(est_par_df_full_3, aes(y=par_val, x=par_names))+
    geom_point(
      aes(color = lkl),
      position = position_dodge(0.5),
      size=2
    )+
    geom_errorbar(aes(ymin = CI.inf, ymax = CI.sup, color = lkl),
                  position = position_dodge(0.5),width=0.4
    )+
    scale_color_manual(breaks = c("Scientific model",
                                  "Yi*",
                                  "Dj"),
                       values=c("#619CFF","#F8766D","#00BA38"))+
    geom_hline(yintercept=0, linetype="dashed", color = "red",alpha=0.4)+
    xlab("")+ylab("")+
    theme_bw()+
    ggtitle("Parameters estimates")+
    theme(plot.title = element_text(hjust = 0.5,face = "bold"),
          legend.title = element_blank(),
          legend.position = "bottom",
          aspect.ratio = 1)+
    coord_flip()+
    scale_x_discrete(labels=c('k_com'=parse(text = TeX('$k_{com}$')),
                              'Sigma_com'=parse(text = TeX('$\\sigma_{com}$')),
                              'q1_com'=parse(text = TeX('$\\xi_{com}$')),
                              'Sigma_sci'=parse(text = TeX('$\\sigma_{sci}$')),
                              'q1_sci'=parse(text = TeX('$\\xi_{sci}$')),
                              'Range'="Range",
                              'MargSD'="M. var.",
                              'substr_Mud_sediment'=parse(text = TeX('$\\beta_{S}$')),
                              'intercept'=parse(text = TeX('$\\mu$'))))

  ggsave("images/par_plot.png",width = 6/1.75,height = 7.5/1.75)

```

@@

# Discussion

### Discussion

@@

#

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  10pt,
  ignorenonframetext,
]{beamer}
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{part title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{part title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usetheme[]{Darmstadt}
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Inferring fine scale wild species distribution from spatially aggregated data},
  pdfauthor={Marie-Pierre Etienne, Baptiste Alglave, Kasper Kristensen, Youen Vermard, Mathieu Woillez, Etienne Rivot},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\newif\ifbibliography
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% package -----------------------------------------
\usepackage{graphicx}
\usepackage{rotating}
%\setbeamertemplate{caption}[numbered]
\usepackage{hyperref}
\usepackage{caption}
\usepackage[normalem]{ulem}
%\mode<presentation>
\usepackage{wasysym}
\usepackage{amsmath}
\usepackage{caption}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{pifont}
\usepackage{dashrule}
\usepackage{setspace}
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}

% ----------------------------------------------
\usepackage[style=authoryear,sorting=ynt]{biblatex}
\usepackage[font={small}]{caption}

\captionsetup[figure]{labelformat=empty}% redefines the caption setup of the figures environment in the beamer class.
\usepackage{caption}
\captionsetup[figure]{font=tiny}

\setbeamertemplate{navigation symbols}{}
\institute{06/2022 - AFH}

% logo -----------------------------------------
\newsavebox{\logoA}
\newsavebox{\logoB}
\newsavebox{\logoC}
\savebox{\logoA}{\includegraphics[width=3cm]{images/logo_ifremer.jpg}}
\savebox{\logoB}{\includegraphics[width=3cm]{images/UMR_DECOD.jpg}}
\savebox{\logoC}{\includegraphics[width=3cm]{images/logo_institut_agro.png}}

% \savebox{\logoD}{\includegraphics[width=1.5cm]{images/dtu_logo.jpg}}
% \newsavebox{\logoD}

\titlegraphic{%
  \raisebox{.5\dimexpr\ht\logoB-\ht\logoA}{\usebox{\logoA}}% raise smaller logo into position
  \hspace*{0.75cm}
  \usebox{\logoC}
  \hspace*{0.75cm}%
  % \usebox{\logoC}
  % \hspace*{1cm}%
  \usebox{\logoB}

% ----------------------------------------------

\setbeamertemplate{title page}[empty]

\setbeamerfont{subtitle}{size=\small}

\setbeamercovered{transparent}

\definecolor{BaptisteBlue}{HTML}{6495ED}
\definecolor{SurveyBlue}{HTML}{619CFF}
\definecolor{BaptisteOrange}{HTML}{F39C12}
\definecolor{BaptisteGreen}{HTML}{1E8449}
\definecolor{BaptisteLightGreen}{HTML}{28B463}
\definecolor{BaptisteGrey}{HTML}{A6ACAF}
\definecolor{BaptisteRed}{HTML}{FF2A2A}
\definecolor{BaptisteBrown}{HTML}{D45500}
\definecolor{BaptisteDarkGrey}{HTML}{8C9193}

% ---------------------------------------------------------
% New command

\newcommand{\btVFill}{\vskip0pt plus 1filll}

% % make code-output smaller
% \DefineVerbatimEnvironment{Highlighting}{Verbatim}{fontsize=\tiny,commandchars=\\\{\}}
% 
% % make console-output smaller:
%   \makeatletter
% \def\verbatim{\tiny\@verbatim \frenchspacing\@vobeyspaces \@xverbatim}
% \makeatother
%

% \setlength{\parskip}{0pt}

% \setlength{\OuterFrameSep}{-4pt}
% \makeatletter
% \preto{\@verbatim}{\topsep=-10pt \partopsep=-10pt }
% \makeatother

% ---------------------------------------------------------

% \setbeamercolor{frametitle}{fg=clemsonpurple,bg=white}
% \setbeamercolor{title}{fg=clemsonpurple,bg=white}
% \setbeamercolor{local structure}{fg=clemsonpurple}
% \setbeamercolor{section in toc}{fg=clemsonpurple,bg=white}
% % \setbeamercolor{subsection in toc}{fg=clemsonorange,bg=white}
% \setbeamercolor{item projected}{fg=clemsonpurple,bg=white}
% \setbeamertemplate{itemize item}{\color{clemsonpurple}$\bullet$}
% \setbeamertemplate{itemize subitem}{\color{clemsonpurple}\scriptsize{$\bullet$}}
\let\Tiny=\tiny

\AtBeginPart{}
\AtBeginSection{}
\AtBeginSubsection{}
\AtBeginSubsubsection{}
\setlength{\emergencystretch}{0em}
\setlength{\parskip}{0pt}

\title{Inferring fine scale wild species distribution from spatially aggregated
data}
\author{Marie-Pierre Etienne, Baptiste Alglave, Kasper Kristensen, Youen
Vermard, Mathieu Woillez, Etienne Rivot}
\date{}

\begin{document}
\frame{\titlepage}

\hypertarget{context}{%
\section{Context}\label{context}}

\begin{frame}{Spatial data in ecology}
\protect\hypertarget{spatial-data-in-ecology}{}

@@

\end{frame}

\begin{frame}

\begin{center} \Large
\textbf{How to integrate all these datasources?}
\end{center}
\large

(especially when they do not have the same spatial resolution)
\normalsize

@@

\end{frame}

\hypertarget{material-and-method}{%
\section{Material and method}\label{material-and-method}}

\begin{frame}{Commercial catch declarations data in fishery science}
\protect\hypertarget{commercial-catch-declarations-data-in-fishery-science}{}

@@

\end{frame}

\begin{frame}{Two alternative procedures to reallocate catches}
\protect\hypertarget{two-alternative-procedures-to-reallocate-catches}{}

@@

\end{frame}

\begin{frame}{Two alternative procedures to reallocate catches}
\protect\hypertarget{two-alternative-procedures-to-reallocate-catches-1}{}

\textbf{Punctual observation model} (\(Y_i\))

\scriptsize \(\operatorname{L}(y,\mu,\sigma^2)\) is the lognormal
likelihood for observation \(y\), mean \(\mu\) and variance \(\sigma^2\)

\(Y\) and \(D\) are supposed conditional on S and x \footnotesize

\[
\operatorname{P}\left(Y_i=y_{i} \right) =
\left\{
    \begin{array}{ll}
        p_i & \text { if } y_{i}=0 \\
        \left(1-p_i\right) \cdot \operatorname{L}\left(y_{i },\mu_i=\frac{S(x_i)}{\left(1 - p_i\right)},\sigma^{2} \right) & \text { if } y_{i} > 0
    \end{array}
\right.
\]

\[p_{i}=\exp(-e^\xi .S(x_{i}))\]

@@

\end{frame}

\begin{frame}{Specifying
\(\operatorname{P}\left(D_j=d_{j} \vert d_j > 0 \right)\)}
\protect\hypertarget{specifying-operatornamepleftd_jd_j-vert-d_j-0-right}{}

@@

\[E(D_j \vert d_j > 0)=\frac{\sum_{i \in \mathcal{P}_j} S(x_{i})}{1-\pi_j}\]

\[Var(D_j \vert d_j > 0) = \frac{\sum_{i \in \mathcal{P}_j} Var(Y_{i})}{1-\pi_j} - \frac{\pi_j}{(1-\pi_j)^2}E(D_j)^2\]

\[Var(Y_{i})=\frac{S(x_{i})^2}{1-p_{i}}(e^{\sigma^2}-(1-p_{i}))\]

@@

\end{frame}

\begin{frame}{Simulation-estimation and case study}
\protect\hypertarget{simulation-estimation-and-case-study}{}

@@

\end{frame}

\hypertarget{results}{%
\section{Results}\label{results}}

\begin{frame}{Simulation-estimation}
\protect\hypertarget{simulation-estimation}{}

@@

\end{frame}

\begin{frame}{Case study: Sole in the Bay of Biscay}
\protect\hypertarget{case-study-sole-in-the-bay-of-biscay}{}

@@

\end{frame}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\begin{frame}{Discussion}
\protect\hypertarget{discussion-1}{}

@@

\end{frame}

\hypertarget{section}{%
\section{}\label{section}}

\begin{frame}{}

@@

\end{frame}

\end{document}
